Fly away Peter, come back Paul: the conservation and losses of avian non-coding RNAs

### 2014-03-14 paper/manuscript.tex
Added a summary table to the manuscript.

{\bf TABLE ``AVERAGE'' NUMBER OF ncRNAs IN A BIRD GENOME?}

>>>>

  \subsection*{Table 1 - A summary of ncRNA genes in human, chicken and all bird genomes}

This table contains the total number of annotated ncRNAs from
different RNA types in human, chicken and the median number for each
of the 48 birds. The number of chicken ncRNA that show evidence for
expression is also indicated (the percentage is given in parentheses).

\begin{tabular}{|r|r|r|r|l|}
\hline 
\multicolumn{5}{|l|}{{\bf ncRNA genes in human, chicken and all bird genomes}}\\
\hline 
Number in human & median(48 birds) & Number in chicken & Number in chicken  & RNA type\\
                &            &                   & confirmed with RNA-seq & \\
\hline
62&25.0&34&18 (52.9\%)&Long non-coding RNA\\ 
356&499.5&427&323 (75.6\%)&microRNA\\ 
281&120.0&106&91 (85.8\%)&C/D box snoRNA\\ 
336&85.5&68&49 (72.1\%)&H/ACA box snoRNA\\ 
34&13.0&12&12 (100.0\%)&Small cajal body RNA\\ 
1754&48.5&71&37 (52.1\%)&Major spliceosomal RNA\\ 
58&3.0&6&4 (66.7\%)&Minor spliceosomal RNA\\ 
525&82.0&122&107 (87.7\%)&Cis-regulatory element\\ 
316&6.5&9&5 (55.6\%)&7SK RNA\\ 
1&0.0&2&0 (0.0\%)&Telomerase RNA\\ 
9&0.0&2&1 (50.0\%)&Vault RNA\\ 
892&3.0&3&2 (66.7\%)&Y RNA\\ 
1084&173.5&300&291 (97.0\%)&Transfer RNA\\ 
80&9.5&4&4 (100.0\%)&Transfer RNA pseudogene\\ 
941&3.0&4&4 (100.0\%)&SRP RNA\\ 
607&7.0&22&12 (54.5\%)&Ribosomal RNA\\ 
4&1.0&2&2 (100.0\%)&RNase P/MRP RNA\\ 
\hline
\end{tabular}
